DynaProg for Scala

### 2013-01-20 docs/report/benchmarks.tex
Report nits.

\subsubsection{CPU: DynaProg(Scala), hand optimized C, GAPC and ADPFusion}
XXX

\begin{table}[H]\begin{center}\begin{tabular}{rllll}\toprule
\bf Size	& \bf DynaProg & \bf Optimized C & \bf GAPC & \bf ADP Fusion \\ \midrule
128		&		&		&		& -		\\
256		&		&		&		& -		\\
512		&		&		&		& -		\\
1024	&		&		&		& -		\\
2048	&		&		&		& -		\\
4096	&		&		&		& -		\\
8192	&		&		&		& -		\\ \bottomrule
\end{tabular}
\end{center}
\caption{Matrix chain multiplication results (CPU)}
\end{table}

@@

\subsubsection{GPU: DynaProg(CUDA), hand optimized CUDA, ATLP and GAPC-OpenCL?}
XXX

\subsection{Smith-Watermann}
\subsubsection{CPU: DynaProg(Scala), hand optimized C, GAPC and ADPFusion}
XXX

\subsubsection{GPU: DynaProg(CUDA), hand optimized CUDA, CUDAlign}
XXX

\subsection{Zuker RNA folding}
\subsubsection{CPU: DynaProg(Scala), GAPC, ADPFusion and ViennaRNA}
XXX

\subsubsection{GPU: DynaProg(CUDA), RNAFold?/Lavenier VS ViennaRNA-OpenCL?, GAPC-OpenCL?}
XXX

>>>>

For this problem, we needed to modify the hand optimized version because the memory access was slightly different from the DynaProg version (the original hand-optimized version was storing only the matrix multiplication score whereas the DynaProg version also stores the matrix dimension in intermediate results). Also note that the hand-optimized results are slightly worse than those presented in (\S\ref{baseline_impl}), this is because 64-bit mode is enabled. Because external libraries linked with the Java virtual machine must be in 64 bit, we also enabled this mode in hand-optimized version to maintain a fair comparison, thereby reducing slightly the performance of CUDA operations.
% CPU: DynaProg(Scala), hand optimized C, GAPC and ADPFusion
% GPU: GPU: DynaProg(CUDA), hand optimized CUDA, ATLP and GAPC-OpenCL?

\def\hdr#1#2{\begin{minipage}{3.5cm} {\bf #1} \\[-2pt] \footnotesize #2 \vspace{6pt} \end{minipage}}
\begin{table}[H]\begin{center}{\small\begin{tabular}{llrrrrrrrr}\toprule
& \normalsize\bf Matrix dimension & \normalsize\bf 128 & \normalsize\bf 256 & \normalsize\bf 512 & \normalsize\bf 1024 & \normalsize\bf 2048 & \normalsize\bf 4096 & \normalsize\bf 8192 \\
\midrule \multirow{4}{*}{\rotatebox{90}{\normalsize\bf CPU $\qquad$}}
& \hdr{DynaProg}{Scala version}
	& 			& 			& 			& 			& 			& 			& 		 \\
& \hdr{Optimized}{C, single thread}
	& 			& 			& 			& 			& 			& 			& 		 \\
& \hdr{GAPC}{\cite{gapc_thesis}, C, single thread}
	& 			& 			& 			& 			& 			& 			& 		 \\
& \hdr{ADP Fusion}{\cite{adp_fusion}}
	& 			& 			& 			& 			& 			& 			& 		 \\
\midrule \multirow{4}{*}{\rotatebox{90}{\normalsize\bf GPU $\qquad$}}
& \hdr{DynaProg}{CUDA version}
	& 			& 			& 			& 			& 			& 			& 		 \\
& \hdr{Optimized}{CUDA, multi-thread}
	& 			& 			& 			& 			& 			& 			& 		 \\
& \hdr{ATLP}{\cite{gpu_atlp}, rescaled results}
	& 			& 			& 			& 			& 			& 			& 		 \\
& \hdr{GAPC}{\cite{gapc_thesis}, OpenCL}
	& 			& 			& 			& 			& 			& 			& 		 \\
\\ \bottomrule\end{tabular}}\end{center}
\caption{Running time of matrix chain multiplication (in seconds)}\end{table}

@@

\subsection{Smith-Watermann}
% CPU: DynaProg(Scala), hand optimized C, GAPC and ADPFusion
% GPU: DynaProg(CUDA), hand optimized CUDA, CUDAlign
XXX: to compare appropriately either use 3 matrices or constant gap penalty
XXX: move toward use of 3 matrices

\def\hdr#1#2{\begin{minipage}{3.5cm} {\bf #1} \\[-2pt] \footnotesize #2 \vspace{6pt} \end{minipage}}
\begin{table}[H]\begin{center}{\small\begin{tabular}{llrrrrrrrr}\toprule
& \normalsize\bf Matrix dimension & \normalsize\bf 128 & \normalsize\bf 256 & \normalsize\bf 512 & \normalsize\bf 1024 & \normalsize\bf 2048 & \normalsize\bf 4096 & \normalsize\bf 8192 \\
\midrule \multirow{4}{*}{\rotatebox{90}{\normalsize\bf CPU $\qquad$}}
& \hdr{DynaProg}{Scala version}
	& 			& 			& 			& 			& 			& 			& 		 \\
& \hdr{Optimized}{C, single thread}
	& 			& 			& 			& 			& 			& 			& 		 \\
& \hdr{GAPC}{\cite{gapc_thesis}, C, single thread}
	& 			& 			& 			& 			& 			& 			& 		 \\
& \hdr{ADP Fusion}{\cite{adp_fusion}}
	& 			& 			& 			& 			& 			& 			& 		 \\
\midrule \multirow{4}{*}{\rotatebox{90}{\normalsize\bf GPU $\qquad$}}
& \hdr{DynaProg}{CUDA version}
	& 			& 			& 			& 			& 			& 			& 		 \\
& \hdr{Optimized}{CUDA, multi-thread}
	& 			& 			& 			& 			& 			& 			& 		 \\
& \hdr{CUDAlign}{\cite{swat_linear}, version 2.0}
	& 			& 			& 			& 			& 			& 			& 		 \\
& \hdr{GAPC}{\cite{gapc_thesis}, OpenCL}
	& 			& 			& 			& 			& 			& 			& 		 \\
\\ \bottomrule\end{tabular}}\end{center}
\caption{Running time of Smith-Waterman (in seconds)}\end{table}

\subsection{Zuker RNA folding}
% CPU: DynaProg(Scala), GAPC, ADPFusion and ViennaRNA
% GPU: DynaProg(CUDA), RNAFold?/Lavenier VS ViennaRNA-OpenCL?, GAPC-OpenCL?
XXX
